### 2017-11-28 manuscript.rmd
shows->show
intermediate = uncertainty. Removed Siph_depth_pruned.csv

![Stochastic mapping reconstruction of the evolutionary history of A) palpon zooids, and B) distribution of sexual zooids on the colonies. The color gradients shows the reconstructed probability estimate of the discrete character states along the branches.](figures/Figure5.pdf)

>>>>

![Stochastic mapping reconstruction of the evolutionary history of A) palpon zooids, and B) distribution of sexual zooids on the colonies. The color gradients show the reconstructed probability estimate of the discrete character states along the branches. Intermediate values reflect uncertainty.](figures/Figure5.pdf)
